An open library of human kinase domain constructs for automated bacterial expression

### 2016-02-26 manuscript/ms.tex
Added compressed JPG of kinome tree figure
Add Nick Levinson as coauthor and add basic Acknowledgments.
Edits to manuscript.

\author{Daniel L. Parton}
  \affiliation{Computational Biology Program, Sloan Kettering Institute, Memorial Sloan Kettering Cancer Center, New York, NY 10065}
  \email{daniel.parton@choderalab.org}
\author{Sonya M. Hanson}
  \affiliation{Computational Biology Program, Sloan Kettering Institute, Memorial Sloan Kettering Cancer Center, New York, NY 10065}
  \email{sonya.hanson@choderalab.org}
\author{Lucelenie Rodríguez-Laureano}
  \affiliation{Computational Biology Program, Sloan Kettering Institute, Memorial Sloan Kettering Cancer Center, New York, NY 10065}
  \email{lucelenie.rodriguez@choderalab.org}
\author{Steven K. Albanese}
  \affiliation{Gerstner Sloan Kettering Graduate School, Memorial Sloan Kettering Cancer Center, New York, NY 10065}
  \email{steven.albanese@choderalab.org}
\author{Scott Gradia}
  \affiliation{QB3 MacroLab, University of California, Berkeley, CA 94720}
  \thanks{Current address: Caribou Biosciences, Berkeley, CA 94720}
  \email{sgradia@cariboubio.com}
\author{Chris Jeans}
  \affiliation{QB3 MacroLab, University of California, Berkeley, CA 94720}
  \email{c.jeans@berkeley.edu}
\author{Markus Seeliger}
\affiliation{Department of Pharmacological Sciences, Stony Brook University Medical School, Stony Brook, NY 11794}
\email{markus.seeliger@stonybrook.edu}
\author{John D. Chodera}
 \thanks{Corresponding author}
 \email{john.chodera@choderalab.org}
  \affiliation{Computational Biology Program, Sloan Kettering Institute, Memorial Sloan Kettering Cancer Center, New York, NY 10065}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT/pacs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Kinases play a critical role in cellular signaling pathways.
Human kinase dysregulation has been linked to a number of diseases, such as cancer, diabetes, and inflammation, and as a result, much of the effort in developing treatments (and perhaps 30\% of \emph{all} current drug development effort) has focused on shutting down aberrant kinases with targeted inhibitors.
While insect and mammalian expression systems are frequently utilized for the expression of human kinases, they cannot compete with the simplicity and cost-effectiveness of bacterial expression systems, which historically had found human kinases difficult to express.
Following the demonstration that phosphatase coexpression could give high yields of Src and Abl kinase domains in inexpensive bacterial expression systems~\cite{seeliger:2005:protein-sci:kinase-expression}, we have performed a large-scale expression screen to generate a library of His-tagged human kinase domain constructs that express well in a simple automated bacterial expression system where phosphatase coexpression (YopH for Tyr kinases, lambda for Ser/Thr kinases) is used.
Starting from 96 kinases with crystal structures and any reported bacterial expression, we engineered a library of human kinase domain constructs and screened their coexpression with phosphatase, finding 52 kinases with yields greater than 2 mg/L culture.
All sequences and expression data are provided online at  \url{https://github.com/choderalab/kinase-ecoli-expression-panel}, and the plasmids are in the process of being made available through AddGene.
\end{abstract}

@@

The protein databank (PDB) now contains over 100 human kinases that---according to the PDB data records---were expressed in bacteria.
Since bacterial expression is often complicated by the need to tailor expression and purification protocols individually for each protein expressed, we wondered whether a simple, uniform, automatable expression and purification protocol could be used to express a large number of human kinases to produce a convenient bacterial expression library to facilitate kinase research and selective inhibitor development.
As a first step toward this goal, we developed a structural informatics pipeline to use available kinase structural data and associated metadata to select constructs from available human kinase libraries to clone into a standard set of vectors intended for phosphatase coexpression.
Automated expression screening in Rosetta2 cells found that 52 human kinase domains express with yields greater than 2 mg/L, which should be usable for biochemical, biophysical, screening, and structural biology studies.

All code and source files used in this project can be found at \url{https://github.com/choderalab/kinase-ecoli-expression-panel}, and a convenient sortable table of results can be viewed at \url{http://choderalab.github.io/kinome-data/kinase\_constructs-addgene\_hip\_sgc.html}.

@@

A sortable table of results can be viewed at \url{http://choderalab.github.io/kinome-data/kinase\_constructs-addgene\_hip\_sgc.html}.

@@

Each kinase domain was tagged with a N-terminal His10-TEV and coexpressed with either the truncated YopH164 for Tyr kinases or lambda phosphatase for Ser/Thr kinases.
All construct sequences were cloned into the 2BT10 plasmid, an AMP resistant ColE1 plasmid with a T7 promoter, using LIC (ligation-independent cloning).
The inserts were generated by PCR using the LICv1 forward and reverse tags on the primers (LICv1 FW= TACTTCCAATCCAATGCA; LICv1 RV=  TTATCCACTTCCAATGTTATTA).
Gel purified PCR products were LIC treated with dCTP. 
Plasmid was linearized, gel purified and LIC treated with dGTP.
LIC-treated plasmid and insert were mixed together and transformed into XL1-Blues for plasmid preps.

Expression was performed in Rosetta2 cells grown with Magic Media (Invitrogen autoinducing medium), 100 $\mu$g/mL of carbenicillin and 100 $\mu$g/mL of spectinomycin. 
Single colonies of transformants were cultivated with 900 $\mu$L of MagicMedia into a gas permeable sealed 96-well block. 
The cultures were incubated at 37$^\circ$C for 4 hours and then at 16 $^\circ$C for 40 hours while shaking. 
Next, cells were centrifuged and the pellets were frozen at -80 $^\circ$C overnight. 
Cells were lysed on a rotating platform at room temperature for an hour using 700 $\mu$L of SoluLyse (Genlantis) supplemented with 400 mM NaCl, 20 mM imidazole, 1$\mu$g/mL pepstatin, 1$\mu$g/mL leupeptin and 0.5 mM PMSF.

For protein purification, 500 $\mu$L of the soluble lysate was added to a 25 $\mu$L Ni-NTA resin in a 96-well filter plate. 
Nickel Buffer A (25 mM HEPES pH 7.5, 5\% glycerol, 400 mM NaCl, 20 mM imidazole, 1 mM BME) was added and the plate was shaken for 30 minutes at room temperature. 
The resin was washed with 2 mL of Nickel Buffer A. 
Target proteins were eluted by a 2 hour incubation at room temperature with 10 $\mu$g of TEV protease in 80 $\mu$L of Nickel Buffer A per well and a subsequent wash with 40 $\mu$L of Nickel Buffer A to maximize protein release. 
Nickel Buffer B (25 mM HEPES pH 7.5, 5\% glycerol, 400 mM NaCl, 400 mM imidazole, 1 mM BME) was used to elute TEV resistant material remaining on the resin.
Untagged protein eluted with TEV protease was run on a LabChip GX II Microfluidic system to analyze the major protein species present. 
Samples of total cell lysate, soluble cell lysate and Nickel Buffer B elution were run on a SDS-PAGE for analysis. 
% JDC: I don't recall seeing data from this SDS-PAGE analysis.  Was this actually done?  Where is the data?

We are currently making the library of kinase domain constructs, generated in this work, available for distribution through the plasmid repository \href{https://www.addgene.org/}{Addgene}. 
In the meantime, requests for plasmids can be directed to \url{requests@choderalab.org}.

@@

\begin{figure}[tb]
   \includegraphics[width=\columnwidth]{figures/ncandidates_byfamily.png}
  % JDC: Later, we should use a PDF instead of PNG file for plots
   \caption{{\bf Distribution of kinases in expression test panel by family.}
   Histogram of the 96 kinases in the expression test panel, separated out by kinase family.
   }
  \label{fig:kinases_by_family}
\end{figure}

@@

A panel containing the 96 kinase domain constructs selected through our semi-automated method, was tested for expression in \emph{E. coli}. 
From this initial test, 52 kinase domains showed reasonable expression (yield of more than 2 mg/L in the eluate) (Table~\ref{expression_table}).
While the initial panel of 96 kinases was well-distributed across kinase families, the final most highly expressing (yield of more than 100 ng/$\mu$l eluate) were not as evenly distributed (Figure~\ref{fig:kinome_expression_tree}). 
The 17 most highly expressing kinases showed relatively high purity after elution, though we note that eluting via TEV site cleavage results in a quantity of TEV protease in the eluate (Figure~\ref{fig:caliper_image}).

@@

\caption{{\bf Expression results by kinase.} Yield (determined by Caliper GX II quantitation of the expected size band) reported in ng/$\mu$l eluate, where total eluate volume was 120 $\mu$l from 900 $\mu$L bacterial culture.}

@@

\bf{kinase expressed} & \bf{phosphatase co-expressed} & \bf{concentration (ng/$\mu$l eluate)} \\

@@

MK14\_HUMAN\_D0  & Lambda                    & 530                   \\
VRK3\_HUMAN\_D0  & Lambda                    & 506                   \\
GAK\_HUMAN\_D0   & Lambda                    & 485                   \\
CSK\_HUMAN\_D0   & Truncated YopH164         & 469                   \\
VRK1\_HUMAN\_D0  & Lambda                    & 467                   \\
KC1G3\_HUMAN\_D0 & Lambda                    & 422                   \\
FES\_HUMAN\_D0   & Truncated YopH164         & 330                   \\
PMYT1\_HUMAN\_D0 & Lambda                    & 285                   \\
MK03\_HUMAN\_D0  & Lambda                    & 273                   \\
STK3\_HUMAN\_D0  & Lambda                    & 257                   \\
DYR1A\_HUMAN\_D0 & Lambda                    & 256                   \\
KC1G1\_HUMAN\_D0 & Lambda                    & 256                   \\
MK11\_HUMAN\_D0  & Lambda                    & 238                   \\
MK13\_HUMAN\_D0  & Lambda                    & 238                   \\
EPHB1\_HUMAN\_D0 & Truncated YopH164         & 217                   \\
MK08\_HUMAN\_D0  & Lambda                    & 214                   \\
CDK16\_HUMAN\_D0 & Lambda                    & 202                   \\
EPHB2\_HUMAN\_D0 & Truncated YopH164         & 188                   \\
PAK4\_HUMAN\_D0  & Lambda                    & 179                   \\
CDKL1\_HUMAN\_D0 & Lambda                    & 174                   \\
SRC\_HUMAN\_D0   & Truncated YopH164         & 165                   \\
STK16\_HUMAN\_D0 & Lambda                    & 155                   \\
MAPK3\_HUMAN\_D0 & Lambda                    & 141                   \\
PAK6\_HUMAN\_D0  & Lambda                    & 135                   \\
CSK22\_HUMAN\_D0 & Lambda                    & 134                   \\
MERTK\_HUMAN\_D0 & Truncated YopH164         & 126                   \\
PAK7\_HUMAN\_D0  & Lambda                    & 110                   \\
CSK21\_HUMAN\_D0 & Lambda                    & 109                   \\
EPHA3\_HUMAN\_D0 & Truncated YopH164         & 106                   \\
BMPR2\_HUMAN\_D0 & Lambda                    & 106                   \\
M3K5\_HUMAN\_D0  & Lambda                    & 105                   \\
KCC2G\_HUMAN\_D0 & Lambda                    & 100                   \\
E2AK2\_HUMAN\_D0 & Lambda                    & 87                    \\
MK01\_HUMAN\_D0  & Lambda                    & 84                    \\
CSKP\_HUMAN\_D0  & Lambda                    & 76                    \\
CHK2\_HUMAN\_D0  & Lambda                    & 61                    \\
KC1G2\_HUMAN\_D0 & Lambda                    & 57                    \\
DMPK\_HUMAN\_D0  & Lambda                    & 57                    \\
KCC2B\_HUMAN\_D0 & Lambda                    & 53                    \\
FGFR1\_HUMAN\_D0 & Truncated YopH164         & 46                    \\
KS6A1\_HUMAN\_D1 & Lambda                    & 43                    \\
DAPK3\_HUMAN\_D0 & Lambda                    & 30                    \\
STK10\_HUMAN\_D0 & Lambda                    & 28                    \\
KC1D\_HUMAN\_D0  & Lambda                    & 28                    \\
KC1E\_HUMAN\_D0  & Lambda                    & 26                    \\
NEK1\_HUMAN\_D0  & Lambda                    & 25                    \\
CDK2\_HUMAN\_D0  & Lambda                    & 23                    \\
ABL1\_HUMAN\_D0  & Truncated YopH164         & 19                    \\
DAPK1\_HUMAN\_D0 & Lambda                    & 18                    \\
DYRK2\_HUMAN\_D0 & Lambda                    & 18                    \\
HASP\_HUMAN\_D0  & Lambda                    & 17                    \\
FGFR3\_HUMAN\_D0 & Truncated YopH164         & 17                    \\
EPHB3\_HUMAN\_D0 & Truncated YopH164         & 13                    \\
SLK\_HUMAN\_D0   & Lambda                    & 12                    \\
KCC2D\_HUMAN\_D0 & Lambda                    & 12                    \\
NEK7\_HUMAN\_D0  & Lambda                    & 10                    \\
PHKG2\_HUMAN\_D0 & Lambda                    & 10                    \\
VRK2\_HUMAN\_D0  & Lambda                    & 9                     \\
AAPK2\_HUMAN\_D0 & Lambda                    & 8                     \\
AURKA\_HUMAN\_D0 & Lambda                    & 8                     \\
MARK3\_HUMAN\_D0 & Lambda                    & 8                     \\
KAPCA\_HUMAN\_D0 & Lambda                    & 7                     \\
STK24\_HUMAN\_D0 & Lambda                    & 6                     \\
VGFR1\_HUMAN\_D0 & Truncated YopH164         & 4                     \\
KCC4\_HUMAN\_D0  & Lambda                    & 3                     \\
KCC1G\_HUMAN\_D0 & Lambda                    & 2                     \\
KCC2A\_HUMAN\_D0 & Lambda                    & 2                     \\
FAK2\_HUMAN\_D0  & Truncated YopH164         & 2                     \\             

@@

\begin{figure}[tb]
   \includegraphics[width=\columnwidth]{figures/kinome_expression.png}
  \caption{{\bf Representation of kinase domain expression results on phylogenetic tree.}
  Dark green circles represent kinases with expression above 250 $ng/ \mu l$ eluate.
  Light green circles represent kinases with expression between 100 and 250 $ng/ \mu l$ eluate.
  Yellow circles represent kinases with expression between 50 and 100 $ng/ \mu l$ eluate.
  Yellow circles represent kinases with any expression up to 50 $ng/ \mu l$ eluate.
  Image made with KinMap: \href{http://www.kinhub.org/kinmap}{http://www.kinhub.org/kinmap}. 
   }
  \label{fig:kinome_expression_tree}
\end{figure}

\begin{figure*}[tb]
   \includegraphics[width=\columnwidth]{figures/caliper_image.png}
  \caption{{\bf Synthetic gel image rendering of highest expressing kinases.}
   Caliper GX II synthetic gel image rendering of kinases expressing > 200 $ng/ \mu l$ eluate from microfluidic capillary electrophoresis quantitation.
   }
  \label{fig:caliper_image}
\end{figure*}

@@

>>>>

\author{Daniel L. Parton}
  \affiliation{Computational Biology Program, Sloan Kettering Institute, Memorial Sloan Kettering Cancer Center, New York, NY 10065}
  \email{daniel.parton@choderalab.org}
\author{Sonya M. Hanson}
  \affiliation{Computational Biology Program, Sloan Kettering Institute, Memorial Sloan Kettering Cancer Center, New York, NY 10065}
  \email{sonya.hanson@choderalab.org}
\author{Lucelenie Rodríguez-Laureano}
  \affiliation{Computational Biology Program, Sloan Kettering Institute, Memorial Sloan Kettering Cancer Center, New York, NY 10065}
  \email{lucelenie.rodriguez@choderalab.org}
\author{Steven K. Albanese}
  \affiliation{Gerstner Sloan Kettering Graduate School, Memorial Sloan Kettering Cancer Center, New York, NY 10065}
  \email{steven.albanese@choderalab.org}
\author{Scott Gradia}
  \affiliation{QB3 MacroLab, University of California, Berkeley, CA 94720}
  \thanks{Current address: Caribou Biosciences, Berkeley, CA 94720}
  \email{sgradia@cariboubio.com}
\author{Chris Jeans}
  \affiliation{QB3 MacroLab, University of California, Berkeley, CA 94720}
  \email{c.jeans@berkeley.edu}
\author{Markus Seeliger}
\affiliation{Department of Pharmacological Sciences, Stony Brook University Medical School, Stony Brook, NY 11794}
\email{markus.seeliger@stonybrook.edu}
\author{Nicholas Levinson}
\affiliation{Department of Pharmacology, University of Minnesota, Minneapolis, MN 55455}
\email{nml@umn.edu}
\author{John D. Chodera}
 \thanks{Corresponding author}
 \email{john.chodera@choderalab.org}
  \affiliation{Computational Biology Program, Sloan Kettering Institute, Memorial Sloan Kettering Cancer Center, New York, NY 10065}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT/pacs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Kinases play a critical role in cellular signaling pathways.
Human kinase dysregulation has been linked to a number of diseases, such as cancer, diabetes, and inflammation, and as a result, much of the effort in developing treatments (and perhaps 30\% of \emph{all} current drug development effort) has focused on shutting down aberrant kinases with targeted inhibitors.
While insect and mammalian expression systems are frequently utilized for the expression of human kinases, they cannot compete with the simplicity and cost-effectiveness of bacterial expression systems, which historically had found human kinases difficult to express.
Following the demonstration that phosphatase coexpression could give high yields of Src and Abl kinase domains in inexpensive bacterial expression systems~\cite{seeliger:2005:protein-sci:kinase-expression}, we have performed a large-scale expression screen to generate a library of His-tagged human kinase domain constructs that express well in a simple automated bacterial expression system where phosphatase coexpression (YopH for Tyr kinases, lambda for Ser/Thr kinases) is used.
Starting from 96 kinases with crystal structures and any reported bacterial expression, we engineered a library of human kinase domain constructs and screened their coexpression with phosphatase, finding 52 kinases with yields greater than 2~$\mu$g/mL culture.
All sequences and expression data are provided online at  \url{https://github.com/choderalab/kinase-ecoli-expression-panel}, and the plasmids are in the process of being made available through AddGene.
\end{abstract}

@@

The protein databank (PDB) now contains over 100 human kinases that---according to the PDB data records---were expressed in bacteria.
Since bacterial expression is often complicated by the need to tailor expression and purification protocols individually for each protein expressed, we wondered whether a simple, uniform, automatable expression and purification protocol could be used to express a large number of human kinases to produce a convenient bacterial expression library to facilitate kinase research and selective inhibitor development.
As a first step toward this goal, we developed a structural informatics pipeline to use available kinase structural data and associated metadata to select constructs from available human kinase libraries to clone into a standard set of vectors intended for phosphatase coexpression.
Automated expression screening in Rosetta2 cells found that 52 human kinase domains express with yields greater than 2~$\mu$g/mL culture, which should be usable for biochemical, biophysical, screening, and structural biology studies.

All code and source files used in this project can be found at \url{https://github.com/choderalab/kinase-ecoli-expression-panel}, and a convenient sortable table of results can be viewed at \url{http://choderalab.org/kinome-expression}.

@@

A sortable table of results can be viewed at \url{http://choderalab.org/kinome-expression}.

@@

Each kinase domain was tagged with a N-terminal His10-TEV and coexpressed with either the truncated YopH164 for Tyr kinases or lambda phosphatase for Ser/Thr kinases.
All construct sequences were cloned into the 2BT10 plasmid, an AMP resistant ColE1 plasmid with a T7 promoter, using LIC (ligation-independent cloning).
The inserts were generated by PCR using the LICv1 forward (TACTTCCAATCCAATGCA) and reverse (TTATCCACTTCCAATGTTATTA) tags on the primers.
Gel purified PCR products were LIC treated with dCTP. 
Plasmid was linearized, gel purified, and LIC treated with dGTP.
LIC-treated plasmid and insert were mixed together and transformed into XL1-Blues for plasmid preps.

Expression was performed in Rosetta2 cells grown with Magic Media (Invitrogen autoinducing medium), 100~$\mu$g/mL of carbenicillin and 100~$\mu$g/mL of spectinomycin. 
Single colonies of transformants were cultivated with 900~$\mu$L of MagicMedia into a gas permeable sealed 96-well block. 
The cultures were incubated at 37$^\circ$C for 4 hours and then at 16$^\circ$C for 40~hours while shaking. 
Next, cells were centrifuged and the pellets were frozen at -80$^\circ$C overnight. 
Cells were lysed on a rotating platform at room temperature for an hour using 700 $\mu$L of SoluLyse (Genlantis) supplemented with 400~mM NaCl, 20~mM imidazole, 1~$\mu$g/mL pepstatin, 1~$\mu$g/mL leupeptin and 0.5~mM PMSF.

For protein purification, 500~$\mu$L of the soluble lysate was added to a 25~$\mu$L Ni-NTA resin in a 96-well filter plate. 
Nickel Buffer A (25~mM HEPES pH~7.5, 5\% glycerol, 400~mM NaCl, 20~mM imidazole, 1~mM BME) was added and the plate was shaken for 30 minutes at room temperature. 
The resin was washed with 2 mL of Nickel Buffer A. 
Target proteins were eluted by a 2 hour incubation at room temperature with 10~$\mu$g of TEV protease in 80~$\mu$L of Nickel Buffer A per well and a subsequent wash with 40 $\mu$L of Nickel Buffer A to maximize protein release. 
Nickel Buffer B (25~mM HEPES pH~7.5, 5\% glycerol, 400~mM NaCl, 400~mM imidazole, 1~mM BME) was used to elute TEV resistant material remaining on the resin.
Untagged protein eluted with TEV protease was run on a LabChip GX II Microfluidic system to analyze the major protein species present. 
Samples of total cell lysate, soluble cell lysate and Nickel Buffer B elution were run on a SDS-PAGE for analysis. 
% JDC: I don't recall seeing data from this SDS-PAGE analysis.  Was this actually done?  Where is the data?

We are currently making the library of kinase domain constructs, generated in this work, available for distribution through the plasmid repository \href{https://www.addgene.org/}{Addgene}\footnote{In the meantime, requests for plasmids can be directed to \url{requests@choderalab.org}.}.

@@

\begin{figure}[tb]
   \includegraphics[width=\columnwidth]{figures/ncandidates_byfamily.png}
  % JDC: Later, we should use a PDF instead of PNG file for plots
   \caption{{\bf Distribution of kinases by family in expression test.}
   Histogram of the 96 kinases in the expression test panel, separated by kinase family.
   }
  \label{fig:kinases_by_family}
\end{figure}

@@

A panel containing the 96 kinase domain constructs selected through our semi-automated method, was tested for expression in \emph{E. coli}. 
From this initial test, 52 kinase domains showed reasonable expression (yield of more than 2 ng/$\mu$L eluate, which corresponds to 2~$\mu$g/mL culture) (Table~\ref{expression_table}).
While the initial panel of 96 kinases was well-distributed across kinase families, the final most highly expressing (yield of more than 12~$\mu$g/mL kinase) were not as evenly distributed (Figure~\ref{fig:kinome_expression_tree}). 
The 17 most highly expressing kinases showed relatively high purity after elution, though we note that eluting via TEV site cleavage results in a quantity of TEV protease in the eluate (Figure~\ref{fig:caliper_image}).

@@

\caption{{\bf Expression results by kinase.} 
Kinases are listed by Uniprot designation and whether they were co-expressed with Lambda or truncated YopH165 phosphatase.
Yield (determined by Caliper GX II quantitation of the expected size band) reported in $\mu$g/mL culture, where total eluate volume was 120 $\mu$L from 900 $\mu$L bacterial culture.
$\ddag$ denotes that the second kinase domain of KS6A1\_HUMAN was expressed; all other kinases were the first or only kinase domain occurring in the kinase ORF.}

@@

\bf{kinase} & \bf{phosphatase} & \bf{yield ($\mu$g/mL)} \\

@@

MK14\_HUMAN  & Lambda                    & 70.7                            \\
VRK3\_HUMAN  & Lambda                    & 67.5                            \\
GAK\_HUMAN   & Lambda                    & 64.7                            \\
CSK\_HUMAN   & YopH         & 62.5                            \\
VRK1\_HUMAN  & Lambda                    & 62.3                            \\
KC1G3\_HUMAN & Lambda                    & 56.3                            \\
FES\_HUMAN   & YopH         & 44.0                            \\
PMYT1\_HUMAN & Lambda                    & 38.0                            \\
MK03\_HUMAN  & Lambda                    & 36.4                            \\
STK3\_HUMAN  & Lambda                    & 34.3                            \\
DYR1A\_HUMAN & Lambda                    & 34.1                            \\
KC1G1\_HUMAN & Lambda                    & 34.1                            \\
MK11\_HUMAN  & Lambda                    & 31.7                            \\
MK13\_HUMAN  & Lambda                    & 31.7                            \\
EPHB1\_HUMAN & YopH         & 28.9                            \\
MK08\_HUMAN  & Lambda                    & 28.5                            \\
CDK16\_HUMAN & Lambda                    & 26.9                            \\
EPHB2\_HUMAN & YopH         & 25.1                            \\
PAK4\_HUMAN  & Lambda                    & 23.9                            \\
CDKL1\_HUMAN & Lambda                    & 23.2                            \\
SRC\_HUMAN   & YopH         & 22.0                            \\
STK16\_HUMAN & Lambda                    & 20.7                            \\
MAPK3\_HUMAN & Lambda                    & 18.8                            \\
PAK6\_HUMAN  & Lambda                    & 18.0                            \\
CSK22\_HUMAN & Lambda                    & 17.9                            \\
MERTK\_HUMAN & YopH         & 16.8                            \\
PAK7\_HUMAN  & Lambda                    & 14.7                            \\
CSK21\_HUMAN & Lambda                    & 14.5                            \\
EPHA3\_HUMAN & YopH         & 14.1                            \\
BMPR2\_HUMAN & Lambda                    & 14.1                            \\
M3K5\_HUMAN  & Lambda                    & 14.0                            \\
KCC2G\_HUMAN & Lambda                    & 13.3                            \\
E2AK2\_HUMAN & Lambda                    & 11.6                            \\
MK01\_HUMAN  & Lambda                    & 11.2                            \\
CSKP\_HUMAN  & Lambda                    & 10.1                            \\
CHK2\_HUMAN  & Lambda                    & 8.1                             \\
KC1G2\_HUMAN & Lambda                    & 7.6                             \\
DMPK\_HUMAN  & Lambda                    & 7.6                             \\
KCC2B\_HUMAN & Lambda                    & 7.1                             \\
FGFR1\_HUMAN & YopH         & 6.1                             \\
KS6A1\_HUMAN$^\ddag$ & Lambda                    & 5.7                             \\
DAPK3\_HUMAN & Lambda                    & 4.0                             \\
STK10\_HUMAN & Lambda                    & 3.7                             \\
KC1D\_HUMAN  & Lambda                    & 3.7                             \\
KC1E\_HUMAN  & Lambda                    & 3.5                             \\
NEK1\_HUMAN  & Lambda                    & 3.3                             \\
CDK2\_HUMAN  & Lambda                    & 3.1                             \\
ABL1\_HUMAN  & YopH         & 2.5                             \\
DAPK1\_HUMAN & Lambda                    & 2.4                             \\
DYRK2\_HUMAN & Lambda                    & 2.4                             \\
HASP\_HUMAN  & Lambda                    & 2.3                             \\
FGFR3\_HUMAN & YopH         & 2.3                             \\
EPHB3\_HUMAN & YopH         & 1.7                             \\
SLK\_HUMAN   & Lambda                    & 1.6                             \\
KCC2D\_HUMAN & Lambda                    & 1.6                             \\
NEK7\_HUMAN  & Lambda                    & 1.3                             \\
PHKG2\_HUMAN & Lambda                    & 1.3                             \\
VRK2\_HUMAN  & Lambda                    & 1.2                             \\
AAPK2\_HUMAN & Lambda                    & 1.1                             \\
AURKA\_HUMAN & Lambda                    & 1.1                             \\
MARK3\_HUMAN & Lambda                    & 1.1                             \\
KAPCA\_HUMAN & Lambda                    & 0.9                             \\
STK24\_HUMAN & Lambda                    & 0.8                             \\
VGFR1\_HUMAN & YopH         & 0.5                             \\
KCC4\_HUMAN  & Lambda                    & 0.4                             \\
KCC1G\_HUMAN & Lambda                    & 0.3                             \\
KCC2A\_HUMAN & Lambda                    & 0.3                             \\
FAK2\_HUMAN  & YopH         & 0.3                             \\

@@

\begin{figure}[tb]
   \includegraphics[width=\columnwidth]{figures/kinome_expression.jpg}
  \caption{{\bf Representation of kinase domain expression results on phylogenetic tree.}
  Dark green circles represent kinases with expression above 50~$\mu$g/mL culture yield.
  Light green circles represent kinases with expression between 50 and 12~$\mu$g/mL yield.
  Yellow circles represent kinases with expression between 12 and 7~$\mu$g/mL yield.
  Yellow circles represent kinases with any expression (even below 2~$\mu$g/mL) up to 7~$\mu$g/mL yield.
  Image made with KinMap: \href{http://www.kinhub.org/kinmap}{http://www.kinhub.org/kinmap}. 
   }
  \label{fig:kinome_expression_tree}
\end{figure}

\begin{figure*}[tb]
   \includegraphics[width=\columnwidth]{figures/caliper_image.png}
  \caption{{\bf Synthetic gel image rendering of highest expressing kinases.}
   Caliper GX II synthetic gel image rendering of kinases expressing > 25~$\mu$g/mL culture from microfluidic capillary electrophoresis quantitation.
   }
  \label{fig:caliper_image}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}
\label{section:acknowledgments}

DLP, SMH, LRL, SKA, and JDC acknowledge support from the Sloan Kettering Institute.
JDC and DLP acknowledge partial support from NIH grant P30 CA008748 and the Louis V.~Gerstner Young Investigator Award.
